---
title: "Quick Start Guide - jiebaR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Quick Start Guide - jiebaR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

[Chinese Version]

This is a package for Chinese text segmentation, keyword extraction
and speech tagging.

## Example

### Text Segmentation

You can use `worker()` to initialize a worker, and then use `[]` or `segment()` to do the segmentation.

```{r}
library(jiebaR)

##  Using default settings to initialize a worker.
cutter = worker()

###  Note: Can not display Chinese characters here.

segment( "This is a good day!" , cutter )

## OR cutter["This is a good day!"]

```

You can use file path as input.

```{r}
segment( "./temp.dat" , cutter ) ### Auto encoding detection.
```

You can initialize multiple engines simultaneously.

```r
cutter2 = worker(type  = "mix",
                 dict = "some_path/jieba.dict.utf8",
                 hmm   = "some_path/hmm_model.utf8",
                 user  = "some_path/test.dict.utf8",
                 detect=T,      symbol = F,
                 lines = 1e+05, output = NULL
                 )
cutter2   ### Print information of worker
```

```r
Worker Type:  Mix Segment

Detect Encoding :  TRUE
Default Encoding:  UTF-8
Keep Symbols    :  FALSE
Output Path     :
Write File      :  TRUE
Max Read Lines  :  1e+05

Fixed Model Components:

$dict
[1] "dict/jieba.dict.utf8"

$hmm
[1] "dict/hmm_model.utf8"

$user
[1] "dict/test.dict.utf8"

$detect $encoding $symbol $output $write $lines can be reset.
```

The public settings of the model can be modified by `$` `cutter$symbol = T`. Private settings are fixed when the engine is initialized, and you can get them by `cutter$PrivateVarible`.

```{r}
cutter$encoding
cutter$detect
cutter$detect = F
cutter$detect
```

You can use custom dictionar. jiebaR is able to identify new words, but adding your own new words can ensure a higher accuracy. [imewlconverter] is a good tools for dictionary construction.

```{r}
show_dictpath() ### Show path
?edit_dict()   ### For more information
```

### Speech Tagging

Speech Tagging function `[.tagger` and `tagging` tag each word in a sentence after segmentation, using labels compatible with ictclas.

```{r}
words = "hello world"
tagger = worker("tag")
tagger[words]
```

### Keyword Extraction

Keyword Extraction worker use MixSegment model to cut word and use
 TF-IDF algorithm to find the keywords.

```{r}
keys = worker("keywords", topn = 1)
keys <= "words of fun"
```

### Simhash Distance

Simhash worker can do keyword extraction and find
the keywords from two inputs, and then computes Hamming distance between them.

```{r}
 words = "hello world"
 simhasher = worker("simhash",topn=1)
 simhasher[words]
```

```{r}
distance("hello world" , "hello world!" , simhasher)
```

## More Docs

See https://jiebaR.qinwf.com/

## More Information and Issues

[https://github.com/qinwf/jiebaR](https://github.com/qinwf/jiebaR)

[https://github.com/yanyiwu/cppjieba](https://github.com/yanyiwu/cppjieba)

[Chinese Version]:https://github.com/qinwf/jiebaR
[imewlconverter]:https://github.com/studyzy/imewlconverter
